\documentclass[a4paper,12pt]{article}

\usepackage{url}
\usepackage{parskip}     
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}
\usepackage{tabularx}
\usepackage{enumitem}
\newcolumntype{C}{>{\centering\arraybackslash}X} 
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}
\usepackage{titlesec}                   
\usepackage{multicol}
\usepackage{multirow}
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}
\usepackage{fontawesome5}



\begin{document}

\pagestyle{empty} 

\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{Sammy Sahnine} \\[7.5pt]
\href{https://github.com/sammysahnine}{\raisebox{-0.05\height}\faGithub\ sammysahnine} \ $|$ \ 
\href{https://linkedin.com/in/sammysahnine}{\raisebox{-0.05\height}\faLinkedin\ sammysahnine} \ $|$ \ 
\href{https://www.sammysahnine.com/hack}{\raisebox{-0.05\height}\faGlobe \ sammysahnine.com/hack} \ $|$ \ 
\href{mailto:me@sammysahnine.com}{\raisebox{-0.05\height}\faEnvelope \ me@sammysahnine.com} \ 
\end{tabularx}



\section{Summary}
Hello, I'm Sammy, a second year BSc Computer Science student at  \href{https://www.nottingham.ac.uk/computerscience/index.aspx}{The University of Nottingham}, specialising in Advanced Functional Programming, Image Processing and Robotics. Due to graduate in the summer of 2027, with expected first class honours.

\section{Education}
\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Computer Science with Year in Industry BSc (Hons)} & \hfill 2023 - 2027 \\[3.75pt]
\textit{The University of Nottingham} \\ \\
\multicolumn{2}{@{}X@{}}{
    \begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt]
        \item Year 1 Average of 81\%, First-Class Honours.
        \item 95\% in Programming and Algorithms, involving low-level C programming.
        \item 92\% and 91\% in Computer Fundamentals and Systems and Architecture respectively, involving ARM32 assembly code programming, networking, and servers.
    \end{itemize}
    \end{minipage}

}  
\end{tabularx}

\section{Experience}
\begin{tabularx}{\linewidth}{ @{}l r@{} }

\textbf{Hackathons} & \hfill \textit{Python, C, Assembly Language(s)} \\[3.75pt]
\multicolumn{2}{@{}X@{}}{
     Attendee of multiple hackathons across the UK, creating projects such from simple point-and-click games to breathalysers in a 24 hour timeframe.
}  \\ \\

\textbf{Group Projects} & \hfill \textit{Java, Git, Python} \\[3.75pt]
\multicolumn{2}{@{}X@{}}{
     In the first year of my University course, I took part in a software engineering group project in which myself and 4 others had to use Java to create the backend for a house showcasing website. In my second year, I have been elected Git admin for a year long programming project, with the responsibility of setting up CI/CD pipelines, as well as maintaining and merging branches.
}  \\ \\

\end{tabularx}

\section{Extracurricular}
\begin{tabularx}{\linewidth}{ @{}l r@{} }

\textbf{Mentoring Scheme} & \hfill \textit{} \\[3.75pt]
\multicolumn{2}{@{}X@{}}{
     I was chosen to be a mentor for a group of 20 computer science students entering their first year of University. This involves the responsibility of helping them settle in, as well as provide assistance and tutorials related to the course.
}  \\ \\

\textbf{Volunteering} & \hfill \textit{} \\[3.75pt]
\multicolumn{2}{@{}X@{}}{
     Whilst in secondary school and sixth form, I spent weekends volunteering at my local charity shops helping on the shop floor and sorting surplus stock.
}  \\ \\

\textbf{Grahame Waters Prize for Computer Science} & \hfill \textit{} \\[3.75pt]
\multicolumn{2}{@{}X@{}}{
     Recipient of the Grahame Waters Prize for Computer Science from Parmiters' School and Sixth Form
}  \\ \\

\end{tabularx}


\section{Projects}
\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{SpotiPy Client} & \hfill \textit{Python, Spotify Web API} \\[3.75pt]
\multicolumn{2}{@{}X@{}}{
     A terminal based client for Spotify, built in Python. Using the SpotiPy library, utilising the Spotify Web API. Features include built in audio visualiser, the ability to view playlists and saved albums, and play/pause/skip controls. 
}  \\ \\

\textbf{Messagezoid} & \hfill \textit{Swift, Google Firebase, Git} \\[3.75pt]
\multicolumn{2}{@{}X@{}}{
    An end-to-end encrypted messaging app written in Swift for iOS based devices. Utilises Google Firebase in order to host a NoSQL database to store required information such as user details - profile pictures, usernames, etc. This project was created for my A-Level in Computer Science.
}  \\ \\

\textbf{RemoteCheck} & \hfill \textit{Objective-C, Git} \\[3.75pt]
\multicolumn{2}{@{}X@{}}{
    A minimal and lightweight OS X menu bar app that allows you to see CPU/GPU temperature, drive and network activity, and other system statistics of other Macs on your local network.
}  \\
\end{tabularx}

\section{Technical Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
\textbf{Languages} &  \normalsize{C, Haskell, HTML/CSS, JavaScript, Java, Python 3, SQL (SQLite), Swift/SwiftUI, Objective-C, VHDL}\\
 
\textbf{Libraries and APIs} &  \normalsize{Matplotlib, NumPy, Matplotlib, Firebase, OpenGL, Metal}\\

\textbf{Operating Systems} &  \normalsize{iOS, Mac OS X 10.0 - macOS Sequoia (15), Ubuntu, Windows 98 - 11}\\

\textbf{Developer Tools} &  \normalsize{Docker, Eclipse IDE, Git, GitHub, Google Firebase, IntelliJ IDEA, PyCharm, VS Code, Xcode}\\

\end{tabularx} \\ \\ \\

\center{\footnotesize Last updated: \today}
\center{\footnotesize The latest version of this CV can be found at \href{https://www.sammysahnine.com/cv}{cv.sammysahnine.com}.}

\end{document}